The title

### 2017-11-02 article.tex
Start thm about isure
Removed proof sketch

Given $\ar_3 \mbeats \ar_2, \prop \in \alltopic$: $\ar_3 \wibeatse[\prop] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_2 \nwibeatse[\prop] \ar_3 + \ar_1)] ∨ [\ar_2 \ileadsto \prop ∧ \ar_3 \ibeatse[\prop] \ar_2]$.

@@

\begin{definition}[Observable validity]
	$\forall \ar_2 \mbeats \ar_1 \mleadsto \prop: ¬(\ar_2 \wibeatse[\prop] \ar_1) ∨ \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse[\prop] \ar_2$. Furthermore, if $¬(\clargs \mleadsto ¬\prop), \forall \ar_2 \mbeats \ar_1 \mleadsto \prop: ¬(\ar_2 \wibeatse[\prop, \text{sure}] \ar_1) ∨ \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse[\prop, \text{sure}] \ar_2$.
\end{definition}

\section{Theorem}
\begin{theorem}[Validity]
	Given a decision situation and a model $\eta$, if all our conditions are satisfied, $\mleadsto(\clargs) \subseteq \iposs$.
\end{theorem}
\begin{proof}
Define $\wibeatse^\text{ext} \subseteq \allargs × \allargs$ as: $\ar' \wibeatse^\text{ext} \ar$ iff $\ar' \wibeatse \ar ∨ (\ar \in \mleadstoinv ∧ \ar' \ibeatse \ar)$.

$\ar$ is defended iff its $\wibeatse$-attackers are $\wibeatse$-attacked by $\wibeatse$-decisive arguments.
Sketch:
\begin{enumerate}
	\item $\ar_1$ defended implies $\ar_1$ replaceable by some $\wibeatse$-decisive $\ar$
	\item $\ar_1$ has its $\wibeatse$-attackers $\wibeatse$-attacked by defended arguments implies $\ar_1$ defended
	\item Hence, $\ar_1$ has its $\wibeatse$-attackers $\wibeatse$-attacked by defended arguments implies $\ar_1$ replaceable by $\wibeatse$-decisive
	\item If $\ar_1$ is not defended, it is $\wibeatse$-attacked by no $\ar_2$ decisive [Obs valid], hence, $\ar_1$ is attacked by no $\ar_2$ defended (otherwise there would be a decisive attacker). TODO clarify how we take into account attacks from outside of $\wibeatse$ (simply $\ibeatse$) coming from arguments out of $\clargs$. 
	\item If $\ar_1$ is not defended, it is attacked by some $\ar_2$ attacked by no $\ar_3$ decisive (otherwise, $\ar_1$ defended).
	\item Hence, if $\ar_1$ is not defended, it is attacked by some $\ar_2$ not defended, itself attacked by no $\ar_3$ decisive. And we can hopefully recurse.
	\item In short: $\ar_1$ not defended by dec, attacked by some $\ar_2$ not defended by dec, implies $\ar_2$ attacked by some $\ar_3$ not defended by decisive.
\end{enumerate}
First, we want to prove that $\ar_1$ defended implies $\ar_1$ replaceable by some $\wibeatse$-decisive $\ar$, and if $\ar_1 \in \gdargs$, then its replacer $\ar$ is in $\gdargs$ as well.

>>>>

Given $\ar_3 \mbeats \ar_2, \prop \in \alltopic$: $\ar_3 \wibeatse[\prop] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_2 \nwibeatse[\prop] \ar_3 + \ar_1)] ∨ [\ar_2 \ileadsto \prop ∧ \ar_3 \ibeatse[\prop] \ar_2]$. \footnote{Or $\ar_2 \ileadsto \prop ∧ ¬\prop \notin \mleadsto(\allargs) ∧ \ar_3 \ibeatse[\prop, \text{sure}] \ar_2$.}

@@

\begin{definition}[Observable validity]
	$\forall \ar_2 \mbeats \ar_1 \mleadsto \prop: ¬(\ar_2 \wibeatse[\prop] \ar_1) ∨ \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse[\prop] \ar_2$. Furthermore, if $¬(\clargs \mleadsto \prop), \forall \ar_1 \mleadsto ¬\prop, \ar \in \allargs: \ar_1 \ibeatse[\prop] \ar$.
	\footnote{If the model claims $¬\prop \in \isure$, this requires clear-cut (for that prop), so we must mandate it (hopefully A3 or an equivalent such as Justifiable unstability fits). Thus we only need to prove $\prop \notin \iposs$, for which $\ar_1 \ibeatse[\prop] \ar$ suffices.}
\end{definition}

\section{Theorem}
\begin{theorem}[Validity]
	Given a decision situation and a model $\eta$, if all our conditions are satisfied, $\mleadsto(\clargs) \subseteq \iposs$. Furthermore, if $¬\prop \in \mleadsto(\clargs) ∧ \prop \notin \mleadstoinv(\clargs)$, $¬\prop \in \isure$.
\end{theorem}
\begin{proof}
$\ar$ is defended iff its $\wibeatse$-attackers are $\wibeatse$-attacked by $\wibeatse$-decisive arguments.

First, we want to prove that $\ar_1$ defended implies $\ar_1$ replaceable by some $\wibeatse$-decisive $\ar$, and if $\ar_1 \in \gdargs$, then its replacer $\ar$ is in $\gdargs$ as well.
